---
title: "State of the Practice: Power Provisioning - Power Evaluation of HPCG & HPL"
output:
  html_document:
    df_print: paged
  pdf_document: 
    keep_tex: true
  html_notebook: default
---

# Preparation

We do things in R here.

First of all we clear the environment. Better be save than sorry.

```{r warning=FALSE}
rm(list=ls())
```

Now we load some handy packages.

```{r message=FALSE}
library(ggplot2)
library(lubridate)
library(dplyr)
```

# Data preparation
```{r}
hpl  <- list(uc  = read.csv('./A2_hpl_uc.csv'),
             spc = read.csv('./A2_hpl_spc.csv'),
             dpc = read.csv('./A2_hpl_dpc.csv'))

hpcg <- list(uc  = read.csv("A2_hpcg_uc.csv"),
             spc = read.csv("A2_hpcg_spc.csv"),
             dpc = read.csv("A2_hpcg_dpc.csv"))

df.hpl <- list()

for (c in c("uc","spc","dpc")) {
  df.hpl[[c]] <- data.frame(time  = rep(as.POSIXct(hpl[[c]][,"Time"]),64),
                            power = unlist(hpl[[c]][,2:65]),
                            node  = rep(names(hpl[[c]][,2:65]),
                                        each = dim(hpl[[c]])[1]))
  rownames(df.hpl[[c]]) <- NULL
  df.hpl[[c]] <- df.hpl[[c]] %>% filter(!is.na(power))
}

df.hpcg <- list()

for (c in c("uc","spc","dpc")) {
  df.hpcg[[c]] <- data.frame(time  = rep(as.POSIXct(hpcg[[c]][,"Time"]),64),
                             power = unlist(hpcg[[c]][,2:65]),
                             node  = rep(names(hpcg[[c]][,2:65]),
                                         each = dim(hpcg[[c]])[1]))
  rownames(df.hpcg[[c]]) <- NULL
  df.hpcg[[c]] <- df.hpcg[[c]] %>% filter(!is.na(power))
}
```

# Plot HPL raw data
```{r}

ggplot() + 
  geom_line(data=df.hpl[["uc"]],aes(x=time,y=power,color=node),
            show.legend = FALSE)
ggplot() + 
  geom_line(data=df.hpl[["spc"]],aes(x=time,y=power,color=node),
            show.legend = FALSE)
ggplot() + 
  geom_line(data=df.hpl[["dpc"]],aes(x=time,y=power,color=node),
            show.legend = FALSE)

```

# Plot HCG raw data
```{r}

ggplot() + 
  geom_line(data=df.hpcg[["uc"]],aes(x=time,y=power,color=node),
            show.legend = FALSE)
ggplot() + 
  geom_line(data=df.hpcg[["spc"]],aes(x=time,y=power,color=node),
            show.legend = FALSE)
ggplot() + 
  geom_line(data=df.hpcg[["dpc"]],aes(x=time,y=power,color=node),
            show.legend = FALSE)

```

# Calculate power values presented in table V.

## HPL
```{r}
unlist(
lapply(df.hpl, function(x){ 
  x %>% group_by(node) %>% 
        summarize(node_power = median(power)) %>%
        summarize(total_power = sum(node_power)/1000) 
}))
```

## HPCG
```{r}
unlist(
lapply(df.hpcg, function(x){ 
  x %>% group_by(node) %>% 
        summarize(node_power = median(power)) %>%
        summarize(total_power = sum(node_power)/1000) 
}))
```
# Generate figure 5

## Prepare data for plotting

Hint: We excluded power values originating from broken CMC sensors on
node r9c1t8n3 for the dpc rund as well as node r7c4t4n3 for the uc run 
for better readability of the graph.

```{r message=FALSE}
gg.plt <- list()

for (c in c("uc", "spc", "dpc")) {
  gg.plt[[c]] <- df.hpcg[[c]] %>% 
  filter(node != "Node.r7c4t4n3") %>% 
  mutate(time = round_date(time,unit = "10 sec")) %>%
  group_by(time,node) %>% 
  summarize(n.power.max  = max(power),
            n.power.med  = median(power),
            n.power.min  = min(power)) %>% 
  group_by(time) %>% 
  summarize(power.max  = sum(n.power.max)/1000,
            power.med  = sum(n.power.med)/1000,
            power.min  = sum(n.power.min)/1000) %>% 
  mutate(time = as.integer(time)) %>%
  mutate(time = time-min(time)+1)
}
```

# Generate figure
```{r}
pdf(file = "A2_figure-5.pdf",height = 3)

par(mar=c(5, 5, 4, 6) + 0.1)

colors <- c("UC" = "red", "SPC" = "yellow3", "DPC" = "green2")

ggplot() +
  geom_ribbon(data=gg.plt[["uc"]],
              aes(x=time,ymin=power.min,ymax=power.max),fill="red",
              alpha=0.25) +
  geom_line(data=gg.plt[["uc"]],
            aes(x=time,y=power.min, color="UC"), linewidth=0.2) +
  geom_line(data=gg.plt[["uc"]],
            aes(x=time,y=power.max, color="UC"), linewidth=0.2) +
  geom_line(data=gg.plt[["uc"]],
            aes(x=time,y=power.med, color="UC"), linewidth=0.2) +
  
  geom_ribbon(data=gg.plt[["spc"]],
              aes(x=time,ymin=power.min,ymax=power.max),fill="yellow3",
              alpha=0.25) +
  geom_line(data=gg.plt[["spc"]],
            aes(x=time,y=power.min,color="SPC"), linewidth=0.2) +
  geom_line(data=gg.plt[["spc"]],
            aes(x=time,y=power.max,color="SPC"), linewidth=0.2) +
  geom_line(data=gg.plt[["spc"]],
            aes(x=time,y=power.med,color="SPC"), linewidth=0.2) + 
  
  geom_ribbon(data=gg.plt[["dpc"]],
              aes(x=time,ymin=power.min,ymax=power.max),fill="green2",
              alpha=0.25) +
  geom_line(data=gg.plt[["dpc"]],
            aes(x=time,y=power.min,color="DPC"), linewidth=0.2) +
  geom_line(data=gg.plt[["dpc"]],
            aes(x=time,y=power.max,color="DPC"), linewidth=0.2) +
  geom_line(data=gg.plt[["dpc"]],
            aes(x=time,y=power.med,color="DPC"), linewidth=0.2) +
  
  xlab("Timestamp (secs)")    +
  ylab("Measured Power (kW)") + 
  
  scale_color_manual(values = colors) + 
  theme(legend.title = element_blank(),
        legend.position = c(0.60,0.35),
    # Hide panel borders and remove grid lines
    panel.border = element_blank(),
    panel.grid.major = element_line(linewidth = 0.2, linetype = 'solid',
                                    colour = "gray85"),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", colour = "black"))

dev.off()
```
